Lipid Interactomics Website

### 2025-01-13 IndividualStudies/AT_2025.qmd
Minor updates, new help symbol
New options for hiding details, showing refs

Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz

@@

Chemical Communications

@@

## Abstract

Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria. Here, we synthesized a multifunctionalized PE derivative (1) de-signed to identify PE-binding proteins in intact cells through photo-crosslinking and subsequent isolation and proteomic analysis of the PE-protein conjugates. Due to its aromatic caging group, 1 is initially concentrating in perinuclear membranes. After uncaging, rapid translocation to mitochondria was observed. Hence, the tool is useful for tracking PE location and for determining the PE interactome. A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.

@@

# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
# Read the data to a df
AT_2025_data <- readr::read_csv("DataTables/AT_ChemicalCommunications_2025.csv")

# Pivot the data to be longer
AT_2025_Long <- AT_2025_data |>
	pivot_longer(cols = -gene_name,
				names_to = c(".value", "LipidProbe"),
				names_pattern = "^(logFC|pvalue|hit_annotation)_(.+)$")

>>>>

::: {.callout-note collapse="true"}

## Study details

#### Authors:
Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz

@@

#### Journal:
Chemical Communications

@@

#### Abstract
Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria. Here, we synthesized a multifunctionalized PE derivative (1) de-signed to identify PE-binding proteins in intact cells through photo-crosslinking and subsequent isolation and proteomic analysis of the PE-protein conjugates. Due to its aromatic caging group, 1 is initially concentrating in perinuclear membranes. After uncaging, rapid translocation to mitochondria was observed. Hence, the tool is useful for tracking PE location and for determining the PE interactome. A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.

#### Lipid probes utilized

#### Cell line analyzed

#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
:::

@@

# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
# Read the data to a df

AT_2025_Long <- readr::read_csv("DataTables/AT_ChemicalCommunications_2025_download.csv")

### 2025-01-13 IndividualStudies/SF_2024.qmd
Minor updates, new help symbol
New options for hiding details, showing refs

## Some data wrangling to clean up Scotty's data
SF_2024_data_raw <- readr::read_csv("DataTables/SF_ACS-ChemBio_2024_Limma_results_V3.csv")

## This is a little messy, but converts the raw data Scotty received from Frank and Per to a clean and minimal dataframe.
SF_2024_data <- SF_2024_data_raw |>
	select(gene_name, keep_Huh7, comparison, logFC, pvalue, hit_annotation) |>
	filter(keep_Huh7 == TRUE) |>
	select(-keep_Huh7) |>
	mutate(LipidProbe = case_when(comparison == "Spa_UV - Spa_noUV" ~ "Spa",
															 comparison == "Sph_UV - Sph_noUV" ~ "Sph")) |>
	filter(LipidProbe == "8-3 FA" | LipidProbe == "1-10 FA" | LipidProbe == "Spa" | LipidProbe == "Sph") |>
	select(-comparison) |>
	glimpse()

@@

>>>>

# Opening the datatable for this page
SF_2024_data <- readr::read_csv("DataTables/SF_ACS-Chem-Bio_2024_download.csv")

@@

::: {.callout-note collapse="true"}

## Study details

#### Lipid probes utilized

#### Cell line analyzed

#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
:::

### 2025-01-13 IndividualStudies/SF_2024_B.qmd
New options for hiding details, showing refs

## Some data wrangling to clean up Scotty's data
SF_2024_data_raw <- readr::read_csv("DataTables/SF_ACS-ChemBio_2024_Limma_results_V3.csv")

## This is a little messy, but converts the raw data Scotty received from Frank and Per to a clean and minimal dataframe.
SF_2024_data <- SF_2024_data_raw |>
	select(gene_name, keep_Huh7, comparison, logFC, pvalue, hit_annotation) |>
	filter(keep_Huh7 == TRUE) |>
	select(-keep_Huh7) |>
	mutate(LipidProbe = case_when(comparison == "FA_8_3_UV - FA_8_3_noUV" ~ "8-3 FA",
															 comparison == "FA_1_10_UV - FA_1_10_noUV" ~ "1-10 FA")) |>
	filter(LipidProbe == "8-3 FA" | LipidProbe == "1-10 FA" | LipidProbe == "Spa" | LipidProbe == "Sph") |>
	select(-comparison) |>
	glimpse()

# Organize the hit annotations as factors
SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

@@

@@

### Lipid probes utilized

### Cell line analyzed

### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>

>>>>

# Opening the datatable for this page
SF_2024_data <- readr::read_csv("DataTables/SF_Chem_Comm_2024_download.csv")

# Organizing the hit annotations as factors
SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

@@

::: {.callout-note collapse="true"}

@@

#### Lipid probes utilized

#### Cell line analyzed

#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
:::

### 2025-01-13 TrifunctionalLipidProbesOverview.qmd
Committing EOD
New options for hiding details, showing refs

>>>>

I could use help writing a succinct article here to describe the use of these probes. We can additionally reference prior publications here -- but I think it would be nice to have a novel description with figures for this site.

I have a few example figures, but I am open to using whichever figures seem best -- if that is a new figure, I'll need guidance on what it should look like.

:::{.border}
![](SiteFigures/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
:::

\br

(Here's an example of what references would look like on the site: [@thomasTrifunctionalLipidDerivatives2025; @schultzFlashClickMultifunctionalized2022a; @schultzChemicalToolsLipid2023])

### 2025-01-13 index.qmd
added checkboxes to table
Committing EOD
Wrapping up for the week
New options for hiding details, showing refs

---
title: "LipidInteractomics_Website"
---

This is a Quarto website.

To learn more about Quarto websites visit <https://quarto.org/docs/websites>.

>>>>

---
title: "Lipid Interactomics Website"
---

A blurb about the objective of this site, maybe a gallery of images from select publications to put here.

Possible site names:

* CLiP Database -- **C**lickable **Li**pid **P**roteomics Database

* TriP Database -- **Tri**functional lipid **P**roteome Database

* TriLiP Database -- **Tri**functional **L**ipid **P**roteome: A Resource for Trifunctional Lipid-Based Proteomics Data
